---
title: "Fizzbuzz&Mario_Challange"
output: html_document
date: "2024-07-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Mario Challenge:** In the classic Super Mario games, Mario ends each level by ascending a flight of stairs and leaping off the top to arrive at the castle at the end. (See [here](https://youtu.be/-avspZlbOWU?t=55) for details). We can imagine that each of the bricks of the stairs is a character X.

```         
If the function is called marioStairs() and we pass in the value 4, we would expect to see stairs with a length of 4 and a height of 4:


```

```{r}
for (i in 0:3) {
    for (j in 0:i) {
      cat("X ")
    }
    cat("\n \n")
  }
```

```         

XX

XXX

XXXX
```

\`\`\`

Creating a function that checks an input of type int and returns fizz if the number is a multiple of 3, buzz if the number is a #multiple of 5, and fizzbuzz if the number is a multiple of 3 and 5.

```{r}
fizz_buzz <- function(n) {
    result <- c()
    for (i in 1:n) {
      if (i %% 3 == 0 ) {
        result <- c(result, "Fizz")
      } else if (i %% 3 == 0 && i %% 5 == 0) {
        result <- c(result, "Fizzbuzz")
      } else if (i %% 5 == 0) {
        result <- c(result, "Buzz")
      } else {
        result <- c(result, as.character(i))
      }
    }
    return(result)
}
fizz_buzz(10)
```
